Microlensing as a possible probe of event-horizon structure in quasars

### 2016-10-10 paper1/ms.tex
changes

The first two source profiles that we consider are the uniform disk and symmetric Gaussian source. 
Both of them can be described by a half-light radius $r_{1/2}$ and a total unlensed light flux $S_0$. 
With the two parameters constrained the one-dimensional profiles, as well as the lightcurves of the two source, are completely determined, since no free parameter remains.

The previous statement does not hold for a crescent source.
In the case of the crescent source there are in total five parameters: the integrated flux of the source $S_0$,
 the radii of the bright/dark disk $R_p$/$R_n$ and the displacement of the centers of the two disks on the axes perpendicular and parallel to the caustic $a$ and $b$.

Two of the parameters can be reduced by expressing the results in terms of $S_0$ and $r_{1/2}$. 
The later being determinable for any set of parameters $R_p, R_n$ and $a^2+b^2$. Moreover, one of the displacement 
parameters $b$ has no impact on the one-dimensional profile of the source that results from the projection of the source image on an axis perpendicular to the caustic.

Since the one-dimensional source profile that corresponds to an axis perpendicular to the caustic contains exhaustively all the information regarding the source that can be revealed by the lightcurve, 
the value of the parameter $b$ does not have an effect on the shape of the lightcurve.

Nevertheless, the $b$ parameter is relevant for the calculation of
$r_{1/2}$.  It's qualitative effect is to decrease the value of the
half-light radius when the absolute value of the parameter is
increased.  With two parameters constrained and another irrelevant to
the shape of the lightcurve, two free parameters remain $R_n$ and $a$.
Figure 4 reveals that the lightcurve of a crescent source has more
visible features than the other two light-curves corresponding to the
disc and Gaussian shape. The parameters $R_n$ and $a$ have strong
influences on the shape of the microlensed lightcurve as can be seen
in Figures~\ref{fig:a_var}, \ref{fig:lightcurve_crescent} and
\ref{fig:lightcurve_crescent_back}.  Moreover, the one-dimensional
source profile corresponding to the direction perpendicular to the
caustic reveal four characteristic points. The overlap of each of
these points with the caustic leaves visible features on the
lightcurve at the corresponding instances of time. In timely order,
the instances correspond to the start of the overlap between the
caustic and the bright disk, the start of the overlap between the
caustic and the dark disk, the end of the overlap between the caustic
and dark disk and finally the end of the overlap between the caustic
and the bright disk.

>>>>

The first two source profiles that we consider are the uniform disk and symmetric Gaussian source. 
Both of them can be described by a half-light radius ($r_{1/2}$) and a total unlensed light flux ($S_0$). 
With the two parameters constrained the one-dimensional profiles, as well as the lightcurves of the 
two source, are completely determined, since no free parameter remains.

The previous statement does not hold for a crescent source.
In the case of the crescent source there are in total five parameters: the integrated flux of the source $S_0$,
 the radii of the bright and dark disks and the displacement of the centers of the two disks on the axes perpendicular and parallel to the caustic.

%Two of the parameters can be reduced by expressing the results in 
%terms of $S_0$ and $r_{1/2}$. 
%The later being determinable for any set of parameters 
%$R_p, R_n$ and $a^2+b^2$. Moreover, one of the displacement 
%parameters $b$ has no impact on the one-dimensional profile 
%of the source that results from the projection of the source
% image on an axis perpendicular to the caustic.

Since the one-dimensional source profile that corresponds to an 
axis perpendicular to the caustic contains exhaustively all the 
information regarding the source that can be revealed by the lightcurve, 
the value of the crescent's disks centers displacement parallel to the caustic 
does not have an effect on the shape of the lightcurve.

Nevertheless, the respective displacement is relevant for the calculation of
of the half-light radius.  It's qualitative effect is to 
decrease the value of the
half-light radius when the absolute value of the parameter is
increased.  In contrast to the simpler source shapes discussed before the
crescent has two additional relevant parameters: the radius of the dark 
disk ($R_n$) and the center displacement in the direction
 perpendicular to the caustic $a$.
Figure 4 reveals that the lightcurve of a crescent source has more
visible features than the other two light-curves corresponding to the
disc and Gaussian shape. The parameters $R_n$ and $a$ have strong
influences on the shape of the microlensed lightcurve as can be seen
in Figures~\ref{fig:a_var}, \ref{fig:lightcurve_crescent} and
\ref{fig:lightcurve_crescent_back}.  Moreover, the one-dimensional
source profile corresponding to the direction perpendicular to the
caustic reveal four characteristic points. The overlap of each of
these points with the caustic leaves visible features on the
lightcurve at the corresponding instances of time. In timely order,
the instances correspond to the start of the overlap between the
caustic and the bright disk, the start of the overlap between the
caustic and the dark disk, the end of the overlap between the caustic
and dark disk and finally the end of the overlap between the caustic
and the bright disk.
